\tool: Automated Generation of Diversified Tests for Self-driving Cars from Existing Maps

### 2021-08-20 paper/main.tex
Up to section 4.C. New images and additional references

\begin{figure*}[t]
\minipage{0.32\textwidth}
\includegraphics[width=\linewidth]{images/distance_cubetown_2}
\endminipage\hfill
\minipage{0.32\textwidth}
\includegraphics[width=\linewidth]{images/distance_cubetown_1}
\endminipage\hfill
\minipage{0.32\textwidth}%
  \includegraphics[width=\linewidth]{images/distance_ba_2}
\endminipage
\caption{Examples of trajectories at increasing levels of similarity. We generated the leftmost (dist=$0$) and central (dist=$0.14$) examples from the Cube Town map, while we generated the rightmost example (dist=$1.72$) from the Borregas Avenue map.}
\label{fig:similarity}
\end{figure*}

\subsection{\tool in a Nutshell}
\tool is entirely automatic and can generate test cases that stress the ego-vehicle in many different ways, possibly involving obstacles that partially or completely occlude the lane in which the ego-vehicle is driving.

Given a map in OpenDrive\footnote{\href{https://www.asam.net/standards/detail/opendrive/}{https://www.asam.net/standards/detail/opendrive}}  format, \tool 
\begin{inparaenum}[(1)]
\item identifies the intersections in the map and 
\item generates abstract driving scenarios that force the ego-vehicle to plan legal trajectories to cross those intersections. Next, \item it selects driving scenarios that correspond to quantifiably different trajectories and
\item generates test cases implementing them. 
Finally, \item it generates even more test cases by placing static obstacles, i.e., parked Non-Playable Characters (NPC) vehicles, in front of the ego-vehicle.
\end{inparaenum}

@@

\subsection{Identifying Intersections}
We use the opendrive2lanelet library~\cite{althoff2018automatic} to translate the original maps from the OpenDrive to the lanelets format. As discussed in Section~\ref{subsect:lanelets}, the lanelets organizes its format by relations using follow and adjacent and provides geometrical information (e.g., the shape of each lanelet) and semantic information.

Despite this, its structure does not explicitly capture intersections; hence \tool implements a heuristic to identify them: First, it uses the geometric information about lanelets to identify overlapping lanelets, which are named as a predecessor, an intersection and a successor. Since overlapping lanelets are likely to belong to the same intersection, \tool groups lanelets that (transitively) overlap together, as demonstrated in Figure~\ref{fig:intersection_a}
%
\begin{figure}[H]
  \centering
    \includegraphics[width=0.5\textwidth]{images/intersection01}
  \caption{An example of an intersection constructed by Salvo.}
  \label{fig:intersection_a}
\end{figure}

The intersections identified this way may be incomplete because some of the lanelets that logically belong to large and complex intersections may not overlap with the other lanelets already assigned to those intersections. Therefore, \tool identifies the missing lanelets as those that are adjacent to the lanelets already assigned to an intersection and include them. As a result, having identified the lanelets that compose intersections, \tool proceeded by generating driving scenarios can force the ego-vehicle to cross them.

>>>>

\begin{figure*}[t]
\minipage{0.33\textwidth}
\includegraphics[width=\linewidth]{images/distance_cubetown_2}
\endminipage\hfill
\minipage{0.33\textwidth}
\includegraphics[width=\linewidth]{images/distance_cubetown_1}
\endminipage\hfill
\minipage{0.33\textwidth}%
  \includegraphics[width=\linewidth]{images/distance_ba_2}
\endminipage
\caption{Examples of similar trajectories. In each plot, we compare pairs of trajectories generated by \tool and report their similarity computed using standard metrics such as the iterative Levenshtein distance (IT~Distance) and Cosine similarity. For example, the first two plots result from the Cube Town map and illustrate cases of very similar roads, while the rightmost plot, which results from the Borregas Avenue map, shows partially overlapping trajectories.}
\label{fig:similarity}
\end{figure*}

\subsection{\tool in a Nutshell}
\tool is entirely automatic and can generate test cases that stress the ego-vehicle in many different ways, possibly involving static obstacles that partially or completely occlude the lane in which the ego-vehicle is driving.

Given a map in OpenDrive format \tool \begin{inparaenum}[(1)]
\item identifies the intersections the map contains, 
\item generates abstract driving scenarios that force the ego-vehicle to plan trajectories to cross those intersections safely, \item selects abstract driving scenarios that maximize the diversity of the allegedly planned trajectories, and \item generates executable test cases implementing the selected abstract driving scenarios.
\end{inparaenum}

\tool can also extend the set of generated test cases by reusing existing ones and placing static obstacles, i.e., Non-Playable Characters (NPC) vehicles, in the lane occupied by the ego-vehicle. By doing so \tool achieves two secondary goals: first, it further increases the diversity of the generated tests, as the obstacles force the ego-vehicle to plan new trajectories; second, it allows testing the ego-vehicle's object detection and collision avoidance in addition to route planning and lane-keeping.

@@

\subsection{Identifying Intersections}

\begin{figure}
  \centering
    \includegraphics[width=0.95\columnwidth]{images/overlapping}
  \caption{An example of an intersection constructed by \tool by transitively identifying overlapping lanelets.}
  \label{fig:overlapping}
\end{figure}

\tool uses the opendrive2lanelet library~\cite{althoff2018automatic} to translate the original maps from the OpenDrive format to the lanelets format. As discussed in Section~\ref{subsect:lanelets}, lanelets are connected by relations like `follow` and `adjacent` that define their semantics and provide geometrical information (e.g., their shape). 
However, since the lanelets format lacks a standardized way to capture intersections explicitly, i.e., via formalized relations between lanelets, \tool implements a heuristic to identify them: 
First, it uses geometric information about lanelets to identify overlapping lanelets (\mbox{Figure~\ref{fig:overlapping}-A} and \mbox{Figure~\ref{fig:overlapping}-B}) as they are likely to belong to the same intersection. Second, since not all the lanelets in the same intersection directly overlap with each other, \tool groups together lanelets that \emph{transitively} overlap (\mbox{Figure~\ref{fig:overlapping}-C}).

\begin{figure}
  \centering
    \includegraphics[width=0.95\columnwidth]{images/nonoverlapping}
  \caption{An example of an intersection constructed by \tool by exploiting the relationships among lanelets.}
  \label{fig:nonoverlapping}
\end{figure}

The intersections identified this way may be incomplete because, in some cases, lanelets that logically should belong together do not overlap with the other lanelets already assigned to those intersections. The bolded lanelets in Figure~\ref{fig:nonoverlapping} exemplify two instances of this situation. \tool identifies those missing lanelets by leveraging the relations defining the lanelet network. For example, for the case reported in \mbox{Figure~\ref{fig:nonoverlapping}-A} \tool includes in the intersection Lanelet~$1$ because it is adjacent to a lanelet already assigned to that intersection, i.e., Lanelet~$2$. For the case reported in \mbox{Figure~\ref{fig:nonoverlapping}-B}, instead, \tool includes Lanelet~$1$ because it precedes Lanelet~$2$ that is adjacent to Lanelet~$3$, the successors of a lanelet already assigned to that intersection, i.e., Lanelet~$4$. 
%
Noticeably, the heuristic implemented by \tool to identify intersections exploiting the relations between lanelets and without user input is different from the one proposed by Klischat et al.~\cite{DBLP:conf/itsc/KlischatLHA20} that instead relies on hierarchical clustering and requires the user to specify a minimum size for the intersection.

After identifying the intersections in the map, \tool can generate driving scenarios that force the ego-vehicle to cross them.
